PHQ-4-R - Data Cleaning (Study 2)

### 2024-02-19 study2/analysis/1_cleaning.qmd
update cleaning and data

df <- df |>
  mutate(
    Expe_PHQ4_Anxiety_1 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Anxiety_1 == 0 ~ 0,
        PHQ4_Anxiety_1 == 0.5 ~ 0.34,
        PHQ4_Anxiety_1 == 1 ~ 0.55,
        PHQ4_Anxiety_1 == 2 ~ 0.71,
        PHQ4_Anxiety_1 == 3 ~ 1,
        .default = PHQ4_Anxiety_1
      ), PHQ4_Anxiety_1
    ),
    Expe_PHQ4_Anxiety_2 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Anxiety_2 == 0 ~ 0,
        PHQ4_Anxiety_2 == 0.5 ~ 0.44,
        PHQ4_Anxiety_2 == 1 ~ 0.58,
        PHQ4_Anxiety_2 == 2 ~ 0.71,
        PHQ4_Anxiety_2 == 3 ~ 1,
        .default = PHQ4_Anxiety_2
      ), PHQ4_Anxiety_2
    ),
    Expe_PHQ4_Depression_3 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Depression_3 == 0 ~ 0,
        PHQ4_Depression_3 == 0.5 ~ 0.38,
        PHQ4_Depression_3 == 1 ~ 0.51,
        PHQ4_Depression_3 == 2 ~ 0.62,
        PHQ4_Depression_3 == 3 ~ 1,
        .default = PHQ4_Depression_3
      ), PHQ4_Depression_3
    ),
    Expe_PHQ4_Depression_4 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Depression_4 == 0 ~ 0,
        PHQ4_Depression_4 == 0.5 ~ 0.35,
        PHQ4_Depression_4 == 1 ~ 0.52,
        PHQ4_Depression_4 == 2 ~ 0.66,
        PHQ4_Depression_4 == 3 ~ 1,
        .default = PHQ4_Depression_4
      ), PHQ4_Depression_4
    ),
    Expe_PHQ4_Anxiety = ifelse(
      PHQ4_Condition == "PHQ4 - Revised", datawizard::rescale(Expe_PHQ4_Anxiety_1 + Expe_PHQ4_Anxiety_2, range = c(0, 2), to = c(0, 6)), PHQ4_Anxiety_1 + PHQ4_Anxiety_2
    ),
    Expe_PHQ4_Depression = ifelse(
      PHQ4_Condition == "PHQ4 - Revised", datawizard::rescale(Expe_PHQ4_Depression_3 + Expe_PHQ4_Depression_4, range = c(0, 2), to = c(0, 6)), PHQ4_Depression_3 + PHQ4_Depression_4
    ),
    Expe_PHQ4_Total = Expe_PHQ4_Anxiety + Expe_PHQ4_Depression
  )

# df |>
#   select(starts_with("Expe_PHQ4_"), PHQ4_Condition) |>
#   pivot_longer(cols = -PHQ4_Condition, names_to = "item", values_to = "score") |>
#   ggplot(aes(x = score)) +
#   geom_density(fill="#9C27B0", adjust=1/2)  +
#   facet_grid(item ~ PHQ4_Condition)
```

@@

```{r}
df |>
  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 30, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 30, 30, Experiment_Duration)) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
  geom_point(aes(color = Experimenter, shape = Category)) +
  geom_text(aes(color = Experimenter, label=ifelse(Experiment_Duration < 4.5, as.character(Participant), '')), hjust=-1, vjust=0) +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  guides(shape = "none") +
  ggside::geom_xsidedensity(aes(fill=Experimenter), color=NA, alpha=0.5) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Experiment Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) 
```

@@

```{r}
df$MoodDisorder <- rowSums(select(df, DisorderTreatment_MoodStabilizer, DisorderTreatment_Antidepressant, DisorderTreatment_Anxiolytic))
df$MoodDisorder <- ifelse(df$MoodDisorder > 0, TRUE, FALSE)
```

`r sum(df$MoodDisorder)` participants (`r insight::format_percent(sum(df$MoodDisorder) / nrow(df))`) have a mood disorder, as indexed by the use of a mood stabilizer, antidepressant, or anxiolytic treatment.

>>>>

df <- df |>
  mutate(
    Weighted_PHQ4_Anxiety_1 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Anxiety_1 == 0 ~ 0,
        PHQ4_Anxiety_1 == 0.5 ~ 0.34,
        PHQ4_Anxiety_1 == 1 ~ 0.55,
        PHQ4_Anxiety_1 == 2 ~ 0.71,
        PHQ4_Anxiety_1 == 3 ~ 1,
        .default = PHQ4_Anxiety_1
      ), PHQ4_Anxiety_1
    ),
    Weighted_PHQ4_Anxiety_2 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Anxiety_2 == 0 ~ 0,
        PHQ4_Anxiety_2 == 0.5 ~ 0.44,
        PHQ4_Anxiety_2 == 1 ~ 0.58,
        PHQ4_Anxiety_2 == 2 ~ 0.71,
        PHQ4_Anxiety_2 == 3 ~ 1,
        .default = PHQ4_Anxiety_2
      ), PHQ4_Anxiety_2
    ),
    Weighted_PHQ4_Depression_3 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Depression_3 == 0 ~ 0,
        PHQ4_Depression_3 == 0.5 ~ 0.38,
        PHQ4_Depression_3 == 1 ~ 0.51,
        PHQ4_Depression_3 == 2 ~ 0.62,
        PHQ4_Depression_3 == 3 ~ 1,
        .default = PHQ4_Depression_3
      ), PHQ4_Depression_3
    ),
    Weighted_PHQ4_Depression_4 = ifelse(
      PHQ4_Condition == "PHQ4 - Revised",
      case_when(
        PHQ4_Depression_4 == 0 ~ 0,
        PHQ4_Depression_4 == 0.5 ~ 0.35,
        PHQ4_Depression_4 == 1 ~ 0.52,
        PHQ4_Depression_4 == 2 ~ 0.66,
        PHQ4_Depression_4 == 3 ~ 1,
        .default = PHQ4_Depression_4
      ), PHQ4_Depression_4
    ),
    Weighted_PHQ4_Anxiety = ifelse(
      PHQ4_Condition == "PHQ4 - Revised", datawizard::rescale(Weighted_PHQ4_Anxiety_1 + Weighted_PHQ4_Anxiety_2, range = c(0, 2), to = c(0, 6)), PHQ4_Anxiety_1 + PHQ4_Anxiety_2
    ),
    Weighted_PHQ4_Depression = ifelse(
      PHQ4_Condition == "PHQ4 - Revised", datawizard::rescale(Weighted_PHQ4_Depression_3 + Weighted_PHQ4_Depression_4, range = c(0, 2), to = c(0, 6)), PHQ4_Depression_3 + PHQ4_Depression_4
    ),
    Weighted_PHQ4_Total = Weighted_PHQ4_Anxiety + Weighted_PHQ4_Depression
  )

# df |>
#   select(starts_with("Weighted_PHQ4_"), PHQ4_Condition) |>
#   pivot_longer(cols = -PHQ4_Condition, names_to = "item", values_to = "score") |>
#   ggplot(aes(x = score)) +
#   geom_density(fill="#9C27B0", adjust=1/2)  +
#   facet_grid(item ~ PHQ4_Condition)
```

@@

```{r}
df |>
  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 30, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 30, 30, Experiment_Duration)) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
  geom_point(aes(color = Experimenter, shape = Category)) +
  geom_text(aes(color = Experimenter, label=ifelse(Experiment_Duration < 3, as.character(Participant), '')), hjust=-1, vjust=0) +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  guides(shape = "none") +
  ggside::geom_xsidedensity(aes(fill=Experimenter), color=NA, alpha=0.5) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Experiment Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) 
```

@@

```{r}
df$MoodDisorder <- rowSums(select(df, DisorderTreatment_MoodStabilizer, DisorderTreatment_Antidepressant, DisorderTreatment_Anxiolytic))
df$MoodDisorder <- ifelse(df$MoodDisorder > 0, TRUE, FALSE)
df$DisorderHistory <- ifelse(df$DisorderHistory == "Yes", TRUE, FALSE)
```

`r sum(df$MoodDisorder)` participants (`r insight::format_percent(sum(df$MoodDisorder) / nrow(df))`) have a mood disorder, as indexed by the use of a mood stabilizer, antidepressant, or anxiolytic treatment. `r sum(df$DisorderHistory)` participants (`r insight::format_percent(sum(df$DisorderHistory) / nrow(df))`) reported having a history of mood disorder.
